Harnessing the cloud to understand light: A whitepaper detailing the \MaxwellFDS core solver

### 2013-03-29 thesis/chapter4.tex
Added chapter 4 and appendix 3.

\chapter{Final Result}
\section{Introduction}
Currently, almost all nanophotonic components are designed 
    by hand-tuning a small number of parameters 
    (e.g. waveguide widths and gaps, hole and ring sizes).
However, the realization of 
    increasingly complex, dense, and robust on-chip optical networks
    will require utilizing increasing numbers of parameters
    when designing nanophotonic components.

Opening the design space to include many more parameters
    allows for smaller footprint, higher performance devices by definition,
    since original designs are still included in this parameter space.
Unfortunately, the lack of intuition for what such designs might look like and
    the inability to manually search such a large parameter space
    have greatly hindered the ability to achieve this.

For this reason, we have developed and implemented a computational method
    which is able to use the full parameter space 
    to design linear nanophotonic components in three dimensions.
Critically, our method requires no user intervention or manual tuning.
Instead, a \emph{design-by-specification} scheme is used 
    to produce designs based solely on a user's performance specification.

We show that our method can indeed produce designs 
    which are extremely compact, and, at the same time, highly efficient.
Furthermore, we demonstrate that devices with novel functionality
    are easily designed.
We also show that our method can be used to produce designs
    with extreme robustness to wavelength and temperature shift,
    as well as fabrication error.

Lastly, all our results are produced by simply specifying
    the functionality and performance of the desired device,
    which suggests that our method may indeed by able
    to design \emph{all} linear nanophotonic devices.

\section{Problem formulation}
% Problem statement 
In order to produce designs which utilize the full parameter space,
    and are based solely on the user's performance specification,
    we formulate the design problem in the following way:
\begin{subequations}\begin{align}
    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
        &   z_\text{min} \le z \le z_\text{max}
\end{align} \label{problem}\end{subequations}

@@

    In contrast to typical schemes for optimizing physical structures,
        our formulation actually allows for non-zero physics residuals;
        which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
    Instead, this formulation is what we call an \emph{objective-first} \cite{ob1_wg}
        formulation in that the \emph{design objective} (explained below)
        is prioritized above satisfying physics.

@@

\section{Method of solution}
We employed the alternating directions method of multipliers (ADMM) algorithm 
    \cite{admm}
    in order to solve \eq{problem}.
The ADMM algorithm solves \eq{problem} by iteratively solving for 
    $x_i$, $z$, and a dual variable $u_i$.

@@

@@

\section{Conclusion}
We have developed and implemented a method to design linear nanophotonic structures
    which are fully three-dimensional and multi-modal,
    have very compact footprints,
    exhibit high efficiency, and
    are manufacturable.
We demonstrate this capability by designing various nanophotonic mode converters,
    splitters, hubs, and fiber couplers.
Critically, many, if not all, of these devices have never been demonstrated before
    and cannot be designed by hand.
In contrast, our method allows user to easily design such devices
    by virtue of our design-by-specification scheme.

In addition, we demonstrate the design of a broadband device 
    which is strongly robust to wavelength and temperature shift,
    as well as fabrication error.
We show that such a device has stable operating wavelengths 
    over temperature shifts as large as 905 K,
    or over-/under-etching error of up to 8 nm.
We suggest, based on this design, that wavelength tolerance
    may be a good heuristic to the design of temperature and fabrication-error
    tolerant nanophotonic devices. \\

This work has been supported by the 
    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
% \end{document}

>>>>

\chapter{Nanophotonic computational design} \label{final}
% \section{Introduction}
% Currently, almost all nanophotonic components are designed 
%     by hand-tuning a small number of parameters 
%     (e.g. waveguide widths and gaps, hole and ring sizes).
% However, the realization of 
%     increasingly complex, dense, and robust on-chip optical networks
%     will require utilizing increasing numbers of parameters
%     when designing nanophotonic components.
% Opening the design space to include many more parameters
%     allows for smaller footprint, higher performance devices by definition,
%     since original designs are still included in this parameter space.
% Unfortunately, the lack of intuition for what such designs might look like and
%     the inability to manually search such a large parameter space
%     have greatly hindered the ability to achieve this.
% For this reason, we have developed and implemented a computational method
%     which is able to use the full parameter space 
%     to design linear nanophotonic components in three dimensions.
% Critically, our method requires no user intervention or manual tuning.
% Instead, a \emph{design-by-specification} scheme is used 
%     to produce designs based solely on a user's performance specification.
% We show that our method can indeed produce designs 
%     which are extremely compact, and, at the same time, highly efficient.
% Furthermore, we demonstrate that devices with novel functionality
%     are easily designed.
% We also show that our method can be used to produce designs
%     with extreme robustness to wavelength and temperature shift,
% Lastly, all our results are produced by simply specifying
%     the functionality and performance of the desired device,
%     which suggests that our method may indeed by able
%     to design \emph{all} linear nanophotonic devices.
\section{Problem formulation}
We now develop a method which may indeed be capable of designing 
    linear nanophotonic device which
    are fully three-dimensional and multi-modal,
    exhibit novel functionality,
    have very compact footprints,
    exhibit high efficiency, and
    are manufacturable.
In addition, we also demonstrate the ability to produce structures
    which are strongly robust to wavelength and temperature shift,
    as well as fabrication error.

In order to produce designs which utilize the full parameter space,
    and are based solely on the user's performance specification,
    we use the following final formulation:
\begin{subequations}\begin{align}
    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
        &   z_\text{min} \le z \le z_\text{max}
\end{align} \label{problem}\end{subequations}

@@

    In contrast to typical schemes for optimizing physical structures,
        our formulation actually allows for non-zero physics residuals;
        which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
    Instead, this formulation is what also an \emph{objective-first} \cite{ob1_wg}
        formulation in that the \emph{design objective} (explained below)
        is prioritized above satisfying physics.

@@

\section{Implementation}
We employed the alternating directions method of multipliers (ADMM) algorithm 
    \cite{admm}
    in order to solve \eq{problem}.
The ADMM algorithm solves \eq{problem} by iteratively solving for 
    $x_i$, $z$, and a dual variable $u_i$.

@@

The mathematical details of our implementation are given 
    in appendix~\ref{maths}

@@

% \section{Conclusion}
% We have developed and implemented a method to design linear nanophotonic structures
%     which are fully three-dimensional and multi-modal,
%     have very compact footprints,
%     exhibit high efficiency, and
%     are manufacturable.
% We demonstrate this capability by designing various nanophotonic mode converters,
%     splitters, hubs, and fiber couplers.
% Critically, many, if not all, of these devices have never been demonstrated before
%     and cannot be designed by hand.
% In contrast, our method allows user to easily design such devices
%     by virtue of our design-by-specification scheme.
% 
% In addition, we demonstrate the design of a broadband device 
%     which is strongly robust to wavelength and temperature shift,
%     as well as fabrication error.
% We show that such a device has stable operating wavelengths 
%     over temperature shifts as large as 905 K,
%     or over-/under-etching error of up to 8 nm.
% We suggest, based on this design, that wavelength tolerance
%     may be a good heuristic to the design of temperature and fabrication-error
%     tolerant nanophotonic devices. \\
% 
% \end{document}

### 2013-03-29 thesis/intro.tex
Added chapter 4 and appendix 3.

The organization of this thesis is straightforward: 
    chapters 2-4 detail the incremental steps in achieving
    our final result, which is presented in chapter 5.

>>>>

The organization of this thesis is straightforward: 
    chapters \ref{direct}-\ref{ob-1} detail the incremental steps in achieving
    our final result, which is presented in chapter \ref{final}.
